sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-27 doc/paper.Rmd

# Citizen science count data with a spatially varying effect

@@

```{r owl-fit, warning=FALSE, message=FALSE, cache=TRUE, echo=TRUE, eval=FALSE}
mesh <- make_mesh(snow, xy_cols = c("X", "Y"), cutoff = 1.5)
fit_owls <- sdmTMB(
  count ~ 1 + nao + (1 | year_factor),
  spatial_varying = ~ 0 + nao,     
  family = nbinom2(link = "log"), data = snow, mesh = mesh, 
  time = "year", spatial = "on", spatiotemporal = "IID"
)
```

>>>>

# Spatially varying coefficients applied to citizen-science owl counts

@@

```{r owl-fit, warning=FALSE, message=FALSE, cache=TRUE, echo=TRUE, eval=FALSE}
mesh <- make_mesh(snow, xy_cols = c("X", "Y"), cutoff = 1.5)
fit_owls <- sdmTMB(
  count ~ 1 + nao + (1 | year_factor),
  spatial_varying = ~ 0 + nao,     
  family = nbinom2(link = "log"), data = snow, mesh = mesh, 
  time = "year", spatial = "on", spatiotemporal = "iid"
)
```
